### 2013-05-31 doc/nips2013/introduction.tex
typos

This paper contributes three ideas:
First, in certain cases, these latent moments are exactly the sufficient statistics of
the log-linear model, in which we case use convex optimization directly to obtain the parameters,
resulting in a consistent parameter estimation procedure (\refsec{threeViewMixtureModel}).
Second, in other cases, the latent moments only provide partial information about the parameters,
but we show that this information can be naturally incorporated
using the measurements framework of \citet{liang09measurements} (\refsec{generalModels}).
This provides a natural way to leverage the method of moments when constructing
a consistent estimator is difficult.
Finally, for factorial models, we introduce a new \emph{unshuffling
factorization} procedure to recover parameter estimates (\refsec{factorialModels}).

>>>>

This paper contributes three ideas:
First, in certain cases, these latent moments are exactly the sufficient statistics of
the log-linear model, in which case we use convex optimization directly to obtain the parameters,
resulting in a consistent parameter estimation procedure (\refsec{threeViewMixtureModel}).
Second, in other cases, the latent moments only provide partial information about the parameters,
but we show that this information can be naturally incorporated
using the measurements framework of \citet{liang09measurements} (\refsec{generalModels}).
This provides a natural way to leverage the method of moments when constructing
a consistent estimator is difficult.
Finally, for factorial models, we introduce a new \emph{unshuffling
factorization} procedure to recover parameter estimates (\refsec{factorialModels}).
